---
title: "Optimize the tax on your stock holdings."
author: "Andreas Tyge Møller"
date: "2 jan 2019"
output: 
 md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Calculate your tax easily, and get feedback on how to optimize your tax

Income from stock holdings outside of retirement savings accounts is taxed with
two different tax rates, 27 percent and 42 percent respectively, depending on
which tax bracket the income falls into.

This package allows you to easily import data from Nordnet portfolio accounts.
It then automatically calculates your total taxable income, and provides advice
on actions to take to optimize the long term taxation on your income from stocks.
In order to optimize the tax rate, the income in the lowest tax bracket should
be maximized. Conversely, income in the highest tax bracket should be minimized.

# How it works

First step is to export the entire transaction history from your Nordnet
portfolio account. Then specify the file path for the transactions file.

```{r transactions}
nordnet <- "transaktionsfil.csv"
```

Now with a single function call, calculate your taxable income for every year in
the transactions history:

```{r initiate, echo=FALSE}
pacman::p_load(dplyr, tidyr, purrr, readr, stringr, lubridate, ggplot2,
               kableExtra)
source("CalcYourTax.R", encoding="utf-8")
```
```{r calcyourtax}
tax_income <- calcyourtax(nordnet)
```
```{r output, echo=FALSE}
knitr::kable(tax_income,
             col.names= c("Year", "Profits", "Dividends", "Tax Income",
                         "Bracket limit", "How to optimize", "Amount"),
             align = c("c", "r", "r", "r", "r", "l", "r"),
             digits=0, format="markdown", format.args = list(big.mark = ",")) 
```

So in each of the previous three years I should have realized more gains in
order to maximize my income in the lowest tax bracket. Too bad I didn't have
this tool handy!

# To-do:

* Package functions
* Add additional details for country specific withheld tax rates on dividends
* Add support for DeGiro accounts


